---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-"
)
```

# rindex

All user-provided wavelengths must be given in meters.

## Installation

You can install rindex from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("tjconstant/rindex")
```

## Example

### Searching for a refractive index dataset

```{r search}
library(rindex)

rindex.search("silver")
```

### Retreiving a dataset

Retrieving a dataset is done using the `rindex.get()` function. You must specify the unique `pageid` as found in the search table.

```{r get, R.options=list(max.print = 10)}
rindex.get(pageid = 1)
```

### Interpolation Functions

You can generate a spline-fit for any dataset using `rindex.function()`. For example, to get the interpolated refractive index of silver at 633 nm,

```{r}
Ag <- rindex.function(1)
Ag(633e-9)
```

A comparison of dataset to spline-function is shown below.

```{r}
Ag_data <- rindex.get(1)
wavelengths <- seq(200,1900,, 100) * 1e-9

plot(Ag_data$wavelength, Ag_data$n, 
     xlab = "wavelength (m) - log scale", 
     ylab = "n",
     main = "Refractive Index of Silver (Real part)")
lines(wavelengths, Re(Ag(wavelengths)), col = 2, lwd = 2)

```
