---
title: "Compatability with mlfilms package"
author: "Tom Constant"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Introduction

The `rindex` package is designed to follow the same conventions as the `mlfilms` package for ease of interoperability. The `mlfilms` package calculates the optical response of a material fora stack of thin films. 

As an example, here we import gold's wavelength-dependant refractive index to get the expected reflection from a thin gold film on a prism

## A Thin Gold Film

First, we search for a gold refractive index set in the database, and in this example choose the reported values of gold from Johnson & Christy to create a refractive index function,

```{r}
library(rindex)
head(rindex.search("Ag")) # using head() here just to keep vignette neat.
```

```{r}
gold <- rindex.function(5)
```

This creates a refractive index function `gold()`. This function accepts one parameter, the wavelength(s) in meters, and returns the complex refractive index. For example, at the HeNe wavelength of 633 nm, the refractive index of gold is:

```{r}
gold(633e-9)
```

## Angular Optical Response

Here we define the stack to contain a single layer of gold, with a thickness of 40 nm. We then calculate the optical response at a fixed wavelength (defaults to 633 nm) using the `mlfilms` package.

```{r}
library(mlfilms)

stack <- list(index = gold, thickness = 40e-9)

angle_response <- angle_scan(stack, incident_medium.index = 1.5)
```

Plotting the result, we see the characteristic reflection minima of a surface plasmon resonance.

```{r}
plot(angle_response$angle, angle_response$Reflection, type='l')
```

## Full Optical Response

To see the dispersive nature of the surface plasmon (due to the wavelegth-dependant refractive index of gold), we can calculate the full response using `mlfilms::dispersion_scan()` of the same stack.

```{r}

optical_response <- dispersion_scan(stack, incident_medium.index = 1.5, show.progress = F)

image(x = unique(optical_response$angle),
      y = unique(optical_response$wavelength),
      z = matrix(optical_response$Reflection, ncol = 100),
      xlab = "angle (degrees)", ylab = "wavelength(m)", col = topo.colors(128))
```
